Efficiency

### 2018-01-02 DraftExec.Rnw
add plots

<<setup, include=FALSE, cache=FALSE, echo=FALSE>>=
opts_chunk$set(fig.path='figures/plots-', fig.align='center', fig.show='hold', eval=T, echo=F)
options(replace.assign=TRUE,width=80)
library(tidyverse)
@

@@

>>>>

<<setup, include=FALSE, cache=FALSE, echo=FALSE>>=
opts_chunk$set(fig.path='figures/plots-', fig.align='center', fig.show='hold', eval=T, echo=F)
options(replace.assign=TRUE,width=80)
library(tidyverse)
library(submarines)
@

@@

\section{App Outputs}

Adjustable figures from App.

<<compute, echo=F>>=

df <- read_rds("extdata/default_subs_df.rds")

df <- run_subs(df,
             hotel = 150,
             total.batt = 500,
             batt.dens = 0.14,
             patrol = 2.5,
             max.speed = 18,
             max.power = 7,
             speed = 8,
             power = 1500,
             system = "jet",
             method = "hotel match")

eff_plot_df <- df %>%
  filter(cat %in% c("eff.jet", "eff.prop")) %>%
  mutate(cat = case_when(
    cat ==  "eff.prop" ~ "Propeller",
    cat ==  "eff.jet" ~ "Jet"
  ))

end_plot_df <- df %>%
  filter(cat %in% c("endurance.prop.hour", "endurance.jet.hour")) %>%
  mutate(cat = case_when(
    cat ==  "endurance.prop.hour" ~ "Propeller",
    cat ==  "endurance.jet.hour" ~ "Jet"
  ))

y_max_e <- roundUpNice(max(pull(end_plot_df, val)))

range_plot_df <- df %>%
  filter(cat %in% c("range.prop", "range.jet")) %>%
  mutate(cat = case_when(
    cat ==  "range.prop" ~ "Propeller",
    cat ==  "range.jet" ~ "Jet"
  ))

y_max_r <- roundUpNice(max(pull(range_plot_df, val)))

power_plot_df <- df %>%
  filter(cat %in% c("hotel","power.mob.drawn.jet", "power.mob.req", "power.mob.drawn.prop")) %>%
  mutate(cat = case_when(
    cat == "hotel" ~ "Hotel Load",
    cat ==  "power.mob.drawn.prop" ~ "Propulsion Power Drawn Propeller",
    cat ==  "power.mob.drawn.jet" ~ "Propulsion Power Drawn Jet",
    cat ==  "power.mob.req" ~ "Thrust Power Required"
  ))

y_max_p <- roundUpNice(max(pull(power_plot_df, val)))
@

\begin{figure}
<<plot_eff, echo=FALSE>>=
ggplot(eff_plot_df, aes(x = kts, y = val, col = cat))+
        geom_line()+
        theme_minimal() +
        scale_y_continuous(breaks=seq(0, 1, 0.2),
                           name = "Efficiency") +
        scale_x_continuous(breaks=seq(0, 20, 2))
@
\caption{Efficiency}
\label{fig:Efficiency_plot}
\end{figure}

\begin{figure}
<<plot_end, echo=FALSE>>=
ggplot(end_plot_df, aes(x = kts, y = val, col = cat))+
          geom_line() +
          theme_minimal() +
          scale_y_continuous(breaks=seq(0, y_max_e, (y_max_e/10)),
                             name = "hours") +
          scale_x_continuous(breaks=seq(0, 20, 2)) +
          geom_text(aes(label = round(val, digits = 1)), nudge_y = 2, angle = 45)
@
\caption{Endurance}
\label{fig:Endurance_plot}
\end{figure}

\begin{figure}
<<plot_range, echo=FALSE>>=
ggplot(range_plot_df, aes(x = kts, y = val, col = cat))+
          geom_line()+
          theme_minimal()+
          scale_y_continuous(breaks=seq(0, y_max_r, (y_max_r/10)),
                             name = "nm") +
          scale_x_continuous(breaks=seq(0, 20, 2)) +
          geom_text(aes(label = round(val, digits = 1)), nudge_y = 2, angle = 45)
@
\caption{Range}
\label{fig:Range_plot}
\end{figure}

\begin{figure}
<<plot_power, echo=FALSE>>=
        ggplot(power_plot_df, aes(x = kts, y = val, col = cat))+
          geom_line() +
          theme_minimal() +
          scale_y_continuous(breaks=seq(0, y_max_p, (y_max_p/10)),
                             name = "hours") +
          scale_x_continuous(breaks=seq(0, 20, 2)) +
          geom_text(aes(label = round(val, digits = 1)), nudge_y = 2, angle = 45)
@
\caption{Power}
\label{fig:Power_plot}
\end{figure}
